\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{titling}

\geometry{a4paper, margin=1in}

\title{Snapshot Objectives}
\author{
    Team 7\\
    Clinton Ma\\
    Carlos Amaya Lorenzo\\
    Andrew Panameno-Ramirez\\
    Zhanqi Wang\\
}
\date{December 4, 2025}

\setlength{\droptitle}{6cm}

\pagestyle{fancy}
\fancyhead[L]{Snapshot Objectives}
\fancyhead[R]{Page \thepage}
\fancyfoot[C]{}

\begin{document}

\begin{titlepage}
\maketitle
\thispagestyle{empty}
\end{titlepage}

\section*{Start Objective}

The initial objective of the project is to create the foundation of the mobile application, which would support the needs of Cal State LA students. Key goals include:

\begin{itemize}
    \item Helping students achieve academic success by supporting their mental, physical, and financial needs.
    \item Designing the user interface structure for the mobile app.
    \item Establishing the resources and mental wellness tools within the app.
    \item Estimating the scope of Pacific Clinics’ work and how the app will extend their support.
\end{itemize}

\section*{1st Checkpoint Objective}

The primary objective of Snapshot 2 is to define the app’s features and convert planning into working components. New goals include:

\begin{itemize}
    \item Implementing PHQ-9 and GAD-7 mental health assessments.
    \item Creating a prototype layout for the chatbot screen and resource hub.
    \item Establishing the app’s navigation structure.
    \item Refining the project's direction based on user surveys.
\end{itemize}

\section*{2nd Checkpoint Objective}

The primary objective of Snapshot 3 is to build on previous work by incorporating more functionality. New goals include:

\begin{itemize}
    \item Expanding mental wellness features, such as with mood check-ins.
    \item Implementing backend logic in AWS and Cloudflare for data storage.
    \item Developing the chatbot’s prompting structure to include safety responses.
    \item Improving the user interface based on feedback.
\end{itemize}

\section*{Due Date Checkpoint}

The primary objective of Snapshot 4, or the Due Date Checkpoint, is to refine the application to ensure it is stable and runs without errors. New goals include:

\begin{itemize}
    \item Finalizing core features such as chatbot interaction, quizzes, and helpful resources.
    \item Identifying bugs and usability issues, and fixing them.
    \item Improving visual components, such as user interface adjustments.
\end{itemize}

\end{document}
